Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/results_JCB.tex
Rewrite

To complete our benchmark we also looked at the Bacterial small subunit ribosomal RNA. 
We gathered the seed multiple sequence alignment (MSA) composed of 93 sequences from the Rfam Database 11.0 (Rfam id: RF00177)~\cite{gardner2011rfam}.
Those sequences are between 1461 and 1568 nucleotides long and yield a similarity of $69\%$.

>>>>

To complete our benchmark, we considered the small subunit ribosomal RNA, a molecule wich is of particular interest  in metagenomics an phylogenetics.
We gathered the seed sequences of the bacterial multiple sequence alignment (MSA) retrieved from the RFAM Database 11.0 (Rfam id: RF00177)~\cite{gardner2011rfam}.
This alignment is composed of 93 sequences, ranging between 1461 and 1568 nucleotides long, and yield an average pairwise sequence similarity of $69\%$.
